Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-06 contents/evaluation.tex
Updates from ShareLaTeX

\begin{figure}[t!]
    \centering
    \includegraphics[width=\columnwidth]{resources/Fig_Variance/final}
    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_1}
    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_2}
    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_4}
    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_6}
    % \includegraphics[height=\vfh]{resources/Fig_Variance/variances}
    \caption{Exemplar human pose annotation for left arm among four annotators. Large variance shows the difficulties of have consistent landmarks. Figure best viewed by zooming in.}
    \label{fig:variance}
\end{figure}

@@

\paragraph{Databases \& Error Metrics} In the case of face, we build both models using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{belhumeur2013localizing}. Sparse AAMs were built from the 68 points annotations provided by~\cite{sagonas_iccv_300w_2013}. We use the standard formulation described in~\cite{Cootes2001,Matthews2004}; piecewise affine was used as their motion model. Our dAAMs were built as the pipeline proposed. Results for this experiment are reported over the 224 testing images of the LFPW database using again 68 point ground truth landmark annotations. For this experiment, we report results using pixels intensities (INT) for both models.

For ear experiment, we studied the feasibility of building and fitting statistical deformable models that capture the variability of the human ear. To this end, we collected 605 high resolution images of ears in unconstrained scenarios and annotated them using both a newly defined 55 point annotation scheme for ears and the curve annotations proposed in this paper. Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}. We randomly split the previous database into two disjoint sets of training (500) and testing (105) images. Both models were built using the 500 images training set and their fitting accuracy evaluated on the 105 images of the testing set. Note here that we used the same procedures to build the models as for faces and same error metric for evaluation.

@@

\paragraph{Experiments} CED Curves for this experiment are shown in Figure \ref{fig:daam_benchmark}. We can readily observe that the accuracy achieved by ear models, in terms of the previous normalised point-to-point error measure, is lower than the one achieved by face models. This result is expected due to the more complex structure of the ear shape. Through visual inspection we determined that fitting errors below 0.1 for ears typically look plausible under the previous error measure where fitting errors below 0.6 for faces. Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations. In fact, classic AAM fail to improve the accuracy of the original initialisation on ears. Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.

>>>>

\begin{figure}[t!]
    \centering
    \includegraphics[width=\columnwidth]{resources/Fig_Variance/final}
    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_1}
    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_2}
    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_4}
    % \includegraphics[height=\vfh]{resources/Fig_Variance/image_6}
    % \includegraphics[height=\vfh]{resources/Fig_Variance/variances}
    \caption{Example of human pose annotation for left arm among 4 annotators. The large variance shows the difficulties of having consistent landmarks. Figure best viewed by zooming in.}
    \label{fig:variance}
\end{figure}

@@

\paragraph{Databases \& Error Metrics} In the case of face, we build both models using the 811 training images of the Labelled Faces Parts in-the-Wild (LFPW) \cite{belhumeur2013localizing}. Sparse AAMs were built from the 68 points annotations provided by~\cite{sagonas_iccv_300w_2013}. Our dAAMs were built as described in Step~\ref{sec:step4}. In both cases we build the appearance models using pixel intensities. The results are reported on the 224 images of the LFPW testset.

In the case of the ear, given the lack of publicly available annotated databases, we collected 605 high resolution images from the internet, that were captured under unconstrained conditions. The images were manually annotated with respect to a 55 point sparse annotation mark-up, as well as the curve annotations proposed in this paper. Examples of these two type of ear annotations are shown in Figure \ref{fig:intro}. We randomly split the database into two disjoint sets of training (500) and testing (105) images. The training of the two models was done in the same way as in the face's case.

@@

\paragraph{Results} Cumulative Error Distribution (CED) curves for this experiment are shown in Figure \ref{fig:daam_benchmark}. We can readily observe that the accuracy achieved by ear models, in terms of the previous normalised point-to-point error measure, is lower than the one achieved by face models. This result is expected due to the more complex structure of the ear shape. Through visual inspection we determined that fitting errors below 0.1 for ears typically look plausible under the previous error measure where fitting errors below 0.6 for faces. Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations. In fact, classic AAM fail to improve the accuracy of the original initialisation on ears. Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.
